% !TeX encoding = UTF-8
% !TeX program = pdflatex
% !TeX spellcheck = en_US

\documentclass[LaM,binding=0.6cm,oneside]{sapthesis}

%\documentclass[oneside]{book}

% \usepackage{showframe}

\usepackage{indentfirst}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{todonotes}
\usepackage{rotating}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage[english]{babel}
\usepackage[nottoc,numbib]{tocbibind}
\usepackage[hidelinks]{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{adjustbox}
\hypersetup{pdftitle={Analysis and Classification of 12-channel ECG signal using Edge Computing},pdfauthor={Hafiz Muhammad Hassan}}

% Commands for the titlepage
\title{Analysis and Classification of 12-channel ECG signal using Edge Computing}
\author{Hafiz Muhammad Hassan}
\IDnumber{1873829}
\course[override]{Corso di Laurea Magistrale in Data Science}
\courseorganizer{Facoltà di Ingegneria Dell'Informazione, Informatica e Statistica}
\AcademicYear{2021/2022}

\copyyear{2022}
\advisor{Prof. Ioannis Chatzigiannakis}

\authoremail{hassan.1873829@studenti.uniroma1.it}

\examdate{15 July 2022}
\examiner{Prof. Cuomo Francesca (Presidente)} 
\examiner{Prof. Anagnostopoulos Aristidis} 
\examiner{Prof. Brutti Pierpaolo}  
\examiner{Prof. Chatzigiannakis Ioannis}  
\examiner{Prof. Crespi Mattia} 
\examiner{Prof. Di Lorenzo Paolo}  
\examiner{Prof. Navigli Roberto} 




\begin{document}



\frontmatter

\maketitle
% \dedication{Dedicated to God, my family and my love one}





% \makeatletter
% \renewcommand{\SAP@AbstractLabel}{Abstract}
% \makeatother

\begin{acknowledgments}
\setstretch{1.125}
\parskip=12pt

I want to convey my gratitude to professor Ioannis Chatzigiannakis, my supervisor, for guiding me through thesis project with endeavour and commitment. It was a pleasant and educational journey to work under his leadership. I also extend this acknowledgement to Daniel and Lorella, my colleagues in this thesis, since they made spectacular contributions to this project.

I want to express my gratitude to my girlfriend Hasna, who supported me while developing this thesis with love and patience.

I also want to thank all faculty of data science program because they provided me with that knowledge that made me complete this thesis project. And last but not least, I would also like to thank family and friend for their support and contributions while studying in a foreign country.



\end{acknowledgments}

\tableofcontents

\mainmatter

\setstretch{1.125}
\parskip=5pt

\include{01_Introduction}

\include{02_Cardiological_fundamentals}

\include{03_related_work}

\include{04_analytical_techniques}

\include{05_ECG_classification_experim}

\include{06_conclusions}

\backmatter
% bibliography
\cleardoublepage
\phantomsection
\bibliographystyle{unsrt} % BibTeX style
\bibliography{bibliography} % BibTeX database without .bib extension

\end{document}
